\Title

### 2020-01-21 manuscript/manuscript.tex
Continue writing EQL technique

}
\newcommand{\DOI}{
    doi:\href{https://doi.org/xxx.xxx/xxxxxx}{10.1093/xxx.xxx/xxxxxx}
}
\newcommand{\DOILink}{
    \href{https://doi.org/xxx.xxx/xxxxxx}{doi.org/xxx.xxx/xxxxxx}
}

@@

The Green's equivalent layer theorem states that any harmonic potential field
generated by any three dimensional physical-property distribution can by
reproduced by a continuous two dimensional surface distribution.
This introduces an ambiguity on the distribution that generates
a potential field: multiple physical-property distributions can generate the
same potential field.
This represents an obstacle for determining the true shape and
physical-property distribution that generates the measured potential field.
Nevertheless this ambiguity can also be exploited for developing preprocessing
techniques like interpolating potential field data.

Approximating the continuous distribution by a finite and discrete density
distribution is the basis of the \emph{equivalent sources technique}
\citep{dampney1969}.
The most common approach is to make use of a set of point masses (the
\emph{equivalent sources}) located beneath the observation points.

@@

\begin{equation}
    \mathbf{g}(\mathbf{p}) = \mathbf{A} \mathbf{m},
    \label{eq:linear-problem-g}
\end{equation}

\noindent where $\mathbf{g}(\mathbf{p})$ is the vector containing the measured
field on the points $\mathbf{p}$, $\mathbf{m}$ is the vector containing the
masses of the point sources and $\mathbf{A}$ the \emph{Jacobian matrix}, whose
elements can be obtained as:

\begin{equation}
    a_{ij} = G \frac{1}{|\mathbf{p}_i - \mathbf{q}_j|^2},
    \quad \forall \,\, i = 1, \ldots, N
    \quad \forall \,\, j = 1, \ldots, M.
\end{equation}

@@

Worth noting that solving equation~\ref{eq:linear-problem-g} is equivalent to
an inversion and thus solving an ill-posed problem by nature due to the
non-uniqueness and the instability of the possible solutions.
Therefore is usually needed to add regularization functions in order to obtain
stable solutions \citep{oliveira2013}.
Moreover there's no limitation on the amount of point sources.
The number of sources can either be equal, less or more than the number of
observation points, leading to well, under or overdetermined linear problem,
respectively.

@@

@@

\begin{equation}
    \psi(\mathbf{p}, \mathbf{q})
    =
    \int
    \frac{\delta(\mathbf{p}, \mathbf{q})}{|\mathbf{p} - \mathbf{q}|}
    \textrm{d}v
    =
    \frac{1}{|\mathbf{p} - \mathbf{q}|}
    =
    \frac{1}{r}.
\end{equation}

This shows that the Green's function associated with any harmonic field is
equal to one over the Cartesian distance between the evaluation and the source
points.

Mathematical background of the EQL\@.
How it can be understood in terms of Green's functions problem.
EQL implementation on Harmonica.

>>>>

}
\newcommand{\DOI}{
    doi:\href{https://doi.org/xxx.xxx/xxxxxx}{xxx.xxx/xxxxxx}
}
\newcommand{\DOILink}{
    \href{https://doi.org/xxx.xxx/xxxxxx}{doi.org/xxx.xxx/xxxxxx}
}

@@

The Green's equivalent layer theorem states that any harmonic potential field
generated by any three dimensional physical-property distribution can by
reproduced by a continuous two dimensional surface distribution.
This introduces an ambiguity on the distribution that generates
a potential field: multiple physical-property distributions can generate the
same potential field.
This represents an obstacle for determining the true shape and
physical-property distribution that generates any measured potential field.
Nevertheless this ambiguity can also be exploited for developing preprocessing
techniques like interpolating potential field data.

Approximating the continuous distribution by a finite and discrete density
distribution is the basis of the \emph{equivalent sources technique}
\citep{dampney1969}.
The most common approach is to make use of a set of point sources (the
\emph{equivalent sources}) located beneath the observation points.

@@

\begin{equation}
    \mathbf{g}(\mathbf{p}) = \mathbf{A} \mathbf{m},
\end{equation}

\noindent where $\mathbf{g}(\mathbf{p})$ is the vector containing the measured
field on the points $\mathbf{p}$, $\mathbf{m}$ is the vector containing the
masses of the point sources and $\mathbf{A}$ a matrix whose
elements can be obtained as:

\begin{equation}
    a_{ij} = G \frac{1}{|\mathbf{p}_i - \mathbf{q}_j|^2},
\end{equation}

@@

@@

It's possible to generalize the equivalent sources technique to any harmonic
field through a Green's function problem, regardless the nature of the field.

@@

\begin{equation}
    \psi(\mathbf{p}, \mathbf{q})
    =
    \int
    \frac{\delta(\mathbf{p}, \mathbf{q})}{|\mathbf{p} - \mathbf{q}|}
    \textrm{d}v
    =
    \frac{1}{|\mathbf{p} - \mathbf{q}|}.
\end{equation}

This shows that the Green's function associated with any harmonic field is
equal to the inverse of the Cartesian distance between the evaluation and the
source points.
Thus any harmonic field $V$ can be expressed as \citep[p.~37]{blakely1995}:

\begin{equation}
    V(\mathbf{p})
    =
    \int \psi(\mathbf{p}, \mathbf{q}) \rho(\mathbf{q}) d\mathbf{q}
    =
    \int \frac{\rho(\mathbf{q})}{|\mathbf{p} - \mathbf{q}|}  d\mathbf{q},
\end{equation}

\noindent where $\rho(\mathbf{q})$ is the density distribution of a certain
physical-property evaluated on the point $\mathbf{q}$. This density
distribution can be approximated by a finite and discrete set of point sources
located on $\{\mathbf{q}_1, \ldots, \mathbf{q}_M\}$:

\begin{equation}
    \rho(\mathbf{q}) =
        \sum\limits_{j=1}^{M} c_j \delta(\mathbf{q} - \mathbf{q_j}),
\end{equation}

\noindent where $c_j$ is a coefficient related to the point source located on
$\mathbf{q}_j$, with the same units as the physical-property.
Then the harmonic field $V$ can be approximated by:

\begin{equation}
    V(\mathbf{p})
    \simeq
    \sum\limits_{j=1}^{M} \frac{c_j}{|\mathbf{p} - \mathbf{q}_j|}.
\end{equation}

In case we have measured the value of the harmonic field on points
$\{\mathbf{p}_1, \ldots, \mathbf{p}_N\}$, we can adjust the values of the $c$
coefficients so they satisfy:

\begin{equation}
    V(\mathbf{p}_i)
    =
    \sum\limits_{j=1}^{M} \frac{c_j}{|\mathbf{p}_i - \mathbf{q}_j|}
    \quad \forall i=1,\ldots,N.
\end{equation}

This system of linear equations can be written in an more algebraic way:

\begin{equation}
    V(\mathbf{p}) = \mathbf{A} \mathbf{c}
    \label{eq:linear-problem}
\end{equation}

\noindent where $V(\mathbf{p}$) is a vertical vector containing the measured
values of $V$ on the observation points, $\mathbf{c}$ a vertical vector
containing the $c$ coefficients and $\mathbf{A}$ is the \emph{Jacobian matrix},
whose elements are defined as the Green's function evaluated on each pair of
points $\mathbf{p}$ and $\mathbf{q}$:

\begin{equation}
    a_{ij}
    =
    \psi(\mathbf{p}_i, \mathbf{q}_j)
    =
    \frac{1}{|\mathbf{p}_i - \mathbf{q}_j|}
\end{equation}

Worth noting that solving equation~\ref{eq:linear-problem} is equivalent to
an inversion and thus solving an ill-posed problem by nature due to the
non-uniqueness and the instability of the possible solutions.
Therefore is usually needed to add regularization functions in order to obtain
stable solutions \citep{oliveira2013}.
Moreover there's no limitation on the amount of point sources.
The number of sources can either be equal, less or more than the number of
observation points, leading to well, under or overdetermined linear problem,
respectively.

EQL implementation on Harmonica.
